Self Regulation Ontology Retest Data Report

### 2017-04-21 SRO_Report.Rmd
rearranged time difference graph by median

```{r warning=FALSE, message=FALSE, fig.height=36}
ggplotly(t1_2_difference %>%
           ggplot(aes(dv, difference, label=dv))+
           geom_boxplot()+
           theme_bw()+
           xlab("")+
           ylab("Standardized difference")+
           coord_flip())
```

>>>>

```{r warning=FALSE, message=FALSE, fig.height=36}
t1_2_difference %>%
           ggplot(aes(reorder(dv, difference, FUN=median), difference))+
           geom_hline(yintercept = 0,color='red',size=1)+
           geom_boxplot()+
           theme_bw()+
           xlab("")+
           ylab("Standardized difference")+
           coord_flip()
```
